\documentclass[12pt,a4paper]{article}

% Packages for style
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{lmodern} % Modern font
\usepackage{xcolor} % Colors
\usepackage{geometry} % Margins
\usepackage{graphicx} % Images
\usepackage{tcolorbox} % Colored boxes
\usepackage{amsmath} % Math support

\geometry{margin=2.5cm}

\begin{document}

% Main welcome header
\begin{tcolorbox}[colback=green!8!white,colframe=green!50!black,title=\Huge AutomaTeX Quick Tour,sharp corners]
\begin{center}
\Large \textbf{Interactive LaTeX Editor with LLM Power} \\
\vspace{0.3cm}
\normalsize \textit{(Strongly advised to read - takes 2 minutes, saves hours)}
\end{center}
\end{tcolorbox}


\vspace{0.8cm}

% Live Preview Demo
\begin{tcolorbox}[colback=blue!5!white,colframe=blue!40!black,title=\textbf{Live Preview Magic},left=5mm,right=5mm]
\textbf{What you see is what you get:} This PDF updates \textit{instantly} in RAM as you type.

\textbf{Try this now}:Change the word "Magic" above to "Power" - watch the preview refresh automatically!

\textbf{Theme sync:} Switch themes (File → Settings) and notice how PDF colors adapt to your preference.
\end{tcolorbox}

\vspace{0.5cm}

% LLM Features Demo
\begin{tcolorbox}[colback=orange!8!white,colframe=orange!50!black,title=\textbf{LLM Assistant Sidebar},left=5mm,right=5mm]
Open any LLM panel on the right sidebar and experience:

• \textbf{Generation:} Create content from prompts \\
• \textbf{Proofreading:} Instant grammar and style fixes \\
• \textbf{Rephrase:} Alternative phrasings for clarity \\

\textbf{Test it:} Select this text, open Proofreading panel, and see LLM suggestions appear instantly.P
\end{tcolorbox}

\vspace{0.5cm}

% Debug System Demo
\begin{tcolorbox}[colback=red!8!white,colframe=red!40!black,title=\textbf{Smart Error Detection},left=5mm,right=5mm]
\textbf{Break something intentionally:} Delete the closing \verb|{| from \verb|\textbf{test}| below:

\textbf{test} ← Remove the \verb|}| and watch LLM analyze the error with helpful suggestions.

\textbf{Quick recovery:} Use Compare feature to restore the last working version instantly.
\end{tcolorbox}

\vspace{0.5cm}

% Shortcuts Demo
\begin{tcolorbox}[colback=purple!8!white,colframe=purple!40!black,title=\textbf{Power User Shortcuts},left=5mm,right=5mm]
Master these time-savers:

• \textbf{Ctrl+B}: Bold selected text → \textbf{bold text} \\
• \textbf{Ctrl+I}: Italicize → \textit{italic text} \\
• \textbf{Ctrl+Shift+M}: Math mode → $E = mc^2$ \\
• \textbf{F5}: Instant compilation \\
• \textbf{Ctrl+F}: Search with live highlighting

\textbf{Try now:} Select any text above and press Ctrl+B to see instant LaTeX formatting.
\end{tcolorbox}

\vspace{0.5cm}

% Mathematical capabilities
\begin{tcolorbox}[colback=teal!8!white,colframe=teal!40!black,title=\textbf{Math Mode Excellence},left=5mm,right=5mm]
Enhanced math support with LLM assistance:

Inline: $\int_0^\infty e^{-x^2} dx = \frac{\sqrt{\pi}}{2}$

Display mode:
\begin{equation}
\sum_{n=1}^{\infty} \frac{1}{n^2} = \frac{\pi^2}{6}
\end{equation}

\textbf{LLM math help:} Use Generation panel with "math mode" for complex equations and proofs.
\end{tcolorbox}

\vspace{0.8cm}

% Call to action
\begin{center}
\begin{tcolorbox}[colback=yellow!10!white,colframe=orange!60!black,title=\textbf{Ready to Explore?},width=0.8\textwidth]
\centering
\textbf{You're 30 seconds away from mastering AutomaTeX}

1. Try one interactive demo above \\
2. Open an LLM sidebar panel \\
3. Create your first document

\vspace{0.3cm}
\textit{The most productive LaTeX session of your life starts now.}
\end{tcolorbox}
\end{center}

\end{document}

