\documentclass[12pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[french]{babel}
\usepackage{graphicx}

\title{La \textit{Ville de Mexico}}
\author{}
\date{}

\begin{document}

\maketitle

\section{\textbf{Mexico City}}

The vibrating heart of \textit{Mexico} beats in its tentacular capital, a city that harmoniously blends ancient history with a dynamic modern spirit.

\textbf{Mexico City}, capital of the \textit{Mexico}, is a dynamic and fascinating metropolis. Its millennial history, impressive architecture and vibrant cultural scene make it a destination of choice.

\subsection*{\textbf{History and Culture}}

Founded by the \textit{Aztecs} au \textbf{14th century} under the name \textit{Tenochtitlan}, the city has been the scene of major historical events, of the conquest \textit{Spanish} to the Revolution \textit{Mexico}Today, it offers an unparalleled cultural richness with its museums, art galleries and living traditions.

\subsection*{\textbf{Architecture}}
    
\textbf{Mexico City} presents a remarkable architectural diversity, ranging from pre-Hispanic remains to colonial buildings and modern skyscrapers.\textit{UNESCO}, houses emblematic monuments such as \textit{Zócalo} and the Metropolitan Cathedral.

\subsection*{\textbf{Gastronomy}}

The gastronomic scene of \textbf{Mexico City} is renowned worldwide. Street stands offering \textit{tacos} and \textit{tamales} at starred restaurants \textit{Michelin}, the city offers a palette of exquisite flavors that reflect the richness of the cuisine \textit{Mexico}.

\subsection*{\textbf{Sites of interest}}

Among the many sites to visit are the \textit{National Museum of Anthropology}, \textit{Palace of Fine Arts}, the neighbourhood of \textit{Coyoacán} with the house of \textit{Frida Kahlo}and the archaeological site of \textit{Teotihuacan}, easily accessible from the city. Architectural diversity continues to charm visitors, who can also enjoy varied cultural activities such as dance and theatre in a city where the\textit{Mexicanidad} is palpable at every corner of the street. \subsection*{\textbf{Transportation}} The public transport system \textbf{Mexico City}, which includes an efficient metro, articulated buses and a well developed road infrastructure, allows residents as well as tourists to easily access various neighborhoods. The city of Mexico City is a cultural and historical jewel where ancestral traditions are associated with modern innovation, making it a must-see destination for all those looking to experience authentic and memorable experiences.
\end{document}





















